Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-11-28 leadership_across_cultures_contexts.Rmd
Minor edits.

Prior to analysis we removed all rows that had no evidence for any variable, which resulted in `r nrow(pca_data_qualities)` text records for the leader quality variables and `r nrow(pca_data_functions)` text records for the leader function variables. We optimized rank, $k$, and a tuning parameter, $m$ (the value to approximate the saturated model), using cross-validation, per recommendation of the package authors.

@@

All analyses were conducted with R version...

@@

@@

For predictor variables we incorporate additional population-level measures. We rely on a modified classification of subsistence from the HRAF, collapsing “hunter-gatherers” and “primarily hunter-gatherers” into a single category, “huntergatherers,” and by collapsing “agro-pastoralists” and “pastoralists” into a single “pastoralists” category. We renamed the eHRAF’s “Other” subsistence category, which is applied to societies with various combinations of hunting, fishing, gathering, pastoralism, and horticulture or intensive agriculture, as “mixed.” This produced a subsistence classification with five groups: Hunter-gatherers, Pastoralists, Horticulturalists, Agriculturalists, and Mixed.

>>>>

Prior to analysis we removed all rows that had no evidence for any variable, which resulted in `r nrow(pca_data_qualities)` text records for the leader quality variables and `r nrow(pca_data_functions)` text records for the leader function variables. We used cross-validation to optimize rank, $k$, and a tuning parameter, $m$ (the value to approximate the saturated model), per recommendation of the package authors.

@@

@@

All analyses were conducted with `r R.version.string`.

@@

For predictor variables we incorporate additional population-level measures. We rely on a modified classification of subsistence from the HRAF, collapsing “hunter-gatherers” and “primarily hunter-gatherers” into a single category, “hunter-gatherers,” and by collapsing “agro-pastoralists” and “pastoralists” into a single “pastoralists” category. We renamed the eHRAF’s “Other” subsistence category, which is applied to societies with various combinations of hunting, fishing, gathering, pastoralism, and horticulture or intensive agriculture, as “mixed.” This produced a subsistence classification with five groups: Hunter-gatherers, Pastoralists, Horticulturalists, Agriculturalists, and Mixed.
